Covariate and differential expression analysis of ROSMAP reprocessed counts Using Diagnosis as a covariate for TWAS

### 2019-09-17 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
SynStore Fix

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn20798014';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
thisFileName <- 'ROSMAP_RegressDiagnosis_4_TWAS.Rmd'
# Github link
thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

@@

# Code WTF is this??
CODE <- Folder(name = "DLPFC - RSEM - EXPECTED COUNTS - GRCh37 - CQN - SVAandDiagnosisRegress - JKG", parentId = parentId)
CODE <- synStore(CODE)

>>>>

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn20798011';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
thisFileName <- 'ROSMAP_RegressDiagnosis_4_TWAS.Rmd'
# Github link
thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

@@

# Code WTF is this??
CODE <- Folder(name = "ROSMAP", parentId = parentId)
CODE <- synStore(CODE)
